Figures and tables for paper

### 2021-12-04 analysis/04_figs-tables.Rmd
Attempt #1 at contrasts with main effects. Hypotheses 4c, 5d and 5e need to be fixed.

```{r}
# Read in interaction draws for contrasts
intib <- read_rds(
    here::here("analysis", "output", "posterior_draws", "interactions.rds")
  )

# Storing intercept draws in a different tibble for easier use; emergency response, no financial transparency, no accountability, many private donors and friendly relationship with government are all reference levels for their respective groups, and thus are not found in the tibble.
dtib <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull()
)
```

@@

```{r crackdown-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_2b.rds")

@@

contrasts_int <- tibble(
  amnesty_criticized = intib %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = intib %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = intib %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = intib %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = intib %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = intib %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = intib %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = intib %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    oxfam_greenpeace_criticized = ((dtib$oxfam + oxfam_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    red_cross_amnesty_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$amnesty + amnesty_criticized) + dtib$criticized),
    red_cross_greenpeace_criticized = ((dtib$red_cross + red_cross_criticized) - (dtib$greenpeace + greenpeace_criticized) + dtib$criticized),
    oxfam_amnesty_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    oxfam_greenpeace_crackdown = ((dtib$oxfam + oxfam_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown),
    red_cross_amnesty_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$amnesty + amnesty_crackdown) + dtib$crackdown),
    red_cross_greenpeace_crackdown = ((dtib$red_cross + red_cross_crackdown) - (dtib$greenpeace + greenpeace_crackdown) + dtib$crackdown)
  )

@@

```{r issue-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_3b.rds")

@@

contrasts_int <- tibble(
  criticized_environment = intib %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = intib %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = intib %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = intib %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = intib %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = intib %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
)

@@

```{r funding-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_4b.rds")

@@

contrasts_int <- tibble(
  criticized_wealthydonors = intib %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = intib %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = intib %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = intib %>% filter(i == 31) %>% select(Gamma) %>% pull(),
)

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_4c.rds")

@@

contrasts_int <- tibble(
  emergency_crackdown_wealthydonors = intib %>% filter(i == 32) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = intib %>% filter(i == 33) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = intib %>% filter(i == 34) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = intib %>% filter(i == 35) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = intib %>% filter(i == 36) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = intib %>% filter(i == 37) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = intib %>% filter(i == 38) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = intib %>% filter(i == 39) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = emergency_crackdown_wealthydonors - humanrights_crackdown_wealthydonors ,
  emergency_environment_wealthydonors = emergency_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  emergency_grants_wealthydonors = emergency_crackdown_wealthydonors - emergency_crackdown_grants,
  refugee_humanrights_wealthydonors = refugee_crackdown_wealthydonors - humanrights_crackdown_wealthydonors,
  refugee_environment_wealthydonors = refugee_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  refugee_grants_wealthydonors = refugee_crackdown_grants - refugee_crackdown_wealthydonors
  )

@@

```{r practices-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5b.rds")

@@

contrasts_int <- tibble(
  financial_transparency_criticized = intib %>% filter(i == 40) %>% select(Gamma) %>% pull(),
  financial_transparency_crackdown = intib %>% filter(i == 41) %>% select(Gamma) %>% pull(),
  )

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5c.rds")

@@

contrasts_int <- tibble(
  fin_smalldonors_criticized = intib %>% filter(i == 42) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = intib %>% filter(i == 43) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = intib %>% filter(i == 44) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = intib %>% filter(i == 45) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = intib %>% filter(i == 46) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = intib %>% filter(i == 47) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = fin_smalldonors_criticized - fin_wealthydonors_criticized,
  fin_smalldonors_grants_criticized = fin_smalldonors_criticized - fin_grants_criticized,
  fin_smalldonors_wealthydonors_crackdown = fin_smalldonors_crackdown - fin_wealthydonors_crackdown,
  fin_smalldonors_grants_crackdown = fin_smalldonors_crackdown - fin_grants_crackdown
  )

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5d.rds")

@@

contrasts_int <- tibble(
  fin_emergency_criticized = intib %>% filter(i == 48) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = intib %>% filter(i == 49) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = intib %>% filter(i == 50) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = intib %>% filter(i == 51) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = intib %>% filter(i == 52) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = intib %>% filter(i == 53) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = intib %>% filter(i == 54) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = intib %>% filter(i == 55) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
)

@@

```{r practices-contrasts-e}
# Overwrite draws with the appropriate interaction data
draws <- here::here("analysis", "output", "posterior_draws", "interactions_5e.rds")

@@

contrasts_int <- tibble(
  fin_sd_emergency_criticized = intib %>% filter(i == 56) %>% select(Gamma) %>% pull(),
  fin_sd_emergency_crackdown = intib %>% filter(i == 57) %>% select(Gamma) %>% pull(),
  fin_sd_environment_criticized = intib %>% filter(i == 58) %>% select(Gamma) %>% pull(),
  fin_sd_environment_crackdown = intib %>% filter(i == 59) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_criticized = intib %>% filter(i == 60) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_crackdown = intib %>% filter(i == 61) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_criticized = intib %>% filter(i == 62) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_crackdown = intib %>% filter(i == 63) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown
)

>>>>

@@

```{r crackdown-contrasts-b}
# Overwrite draws with the appropriate interaction data

draws <- here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds")

@@

contrasts_int <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
    oxfam_greenpeace_criticized = (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
    red_cross_amnesty_criticized = (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
    red_cross_greenpeace_criticized = (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
    oxfam_amnesty_crackdown = (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    oxfam_greenpeace_crackdown = (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
    red_cross_amnesty_crackdown = (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    red_cross_greenpeace_crackdown = (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
  )

@@

```{r issue-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds")

@@

contrasts_int <- tibble(
  criticized_environment = draws %>% filter(i == 22) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws %>% filter(i == 23) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 24) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 25) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws %>% filter(i == 26) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 27) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  criticized_refugee_environment = criticized_refugee - criticized_environment,
  criticized_refugee_humanrights = criticized_refugee - criticized_humanrights,
  crackdown_refugee_environment = crackdown_refugee - crackdown_environment,
  crackdown_refugee_humanrights = crackdown_refugee - crackdown_humanrights
)

@@

```{r funding-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds")

@@

contrasts_int <- tibble(
  criticized_wealthydonors = draws %>% filter(i == 28) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 29) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 30) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 31) %>% select(Gamma) %>% pull(),
)

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds")

@@

contrasts_int <- tibble(
  emergency_crackdown_wealthydonors = draws %>% filter(i == 32) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 33) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 34) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 35) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 36) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 37) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 38) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 39) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = emergency_crackdown_wealthydonors - humanrights_crackdown_wealthydonors ,
  emergency_environment_wealthydonors = emergency_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  emergency_grants_wealthydonors = emergency_crackdown_wealthydonors - emergency_crackdown_grants,
  refugee_humanrights_wealthydonors = refugee_crackdown_wealthydonors - humanrights_crackdown_wealthydonors,
  refugee_environment_wealthydonors = refugee_crackdown_wealthydonors - environment_crackdown_wealthydonors,
  refugee_grants_wealthydonors = refugee_crackdown_grants - refugee_crackdown_wealthydonors
  )

@@

```{r practices-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5b.rds")

@@

contrasts_int <- tibble(
  financial_transparency_criticized = draws %>% filter(i == 40) %>% select(Gamma) %>% pull(),
  financial_transparency_crackdown = draws %>% filter(i == 41) %>% select(Gamma) %>% pull(),
  )

@@

```{r practices-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5c.rds")

@@

contrasts_int <- tibble(
  fin_smalldonors_criticized = draws %>% filter(i == 42) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_criticized = draws %>% filter(i == 43) %>% select(Gamma) %>% pull(),
  fin_grants_criticized = draws %>% filter(i == 44) %>% select(Gamma) %>% pull(),
  fin_smalldonors_crackdown = draws %>% filter(i == 45) %>% select(Gamma) %>% pull(),
  fin_wealthydonors_crackdown = draws %>% filter(i == 46) %>% select(Gamma) %>% pull(),
  fin_grants_crackdown = draws %>% filter(i == 47) %>% select(Gamma) %>% pull(),
  ) %>%
  mutate(
  fin_smalldonors_wealthydonors_criticized = fin_smalldonors_criticized - fin_wealthydonors_criticized,
  fin_smalldonors_grants_criticized = fin_smalldonors_criticized - fin_grants_criticized,
  fin_smalldonors_wealthydonors_crackdown = fin_smalldonors_crackdown - fin_wealthydonors_crackdown,
  fin_smalldonors_grants_crackdown = fin_smalldonors_crackdown - fin_grants_crackdown
  )

@@

```{r practices-contrasts-d}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5d.rds")

@@

contrasts_int <- tibble(
  fin_emergency_criticized = draws %>% filter(i == 48) %>% select(Gamma) %>% pull(),
  fin_emergency_crackdown = draws %>% filter(i == 49) %>% select(Gamma) %>% pull(),
  fin_environment_criticized = draws %>% filter(i == 50) %>% select(Gamma) %>% pull(),
  fin_environment_crackdown = draws %>% filter(i == 51) %>% select(Gamma) %>% pull(),
  fin_humanrights_criticized = draws %>% filter(i == 52) %>% select(Gamma) %>% pull(),
  fin_humanrights_crackdown = draws %>% filter(i == 53) %>% select(Gamma) %>% pull(),
  fin_refugee_criticized = draws %>% filter(i == 54) %>% select(Gamma) %>% pull(),
  fin_refugee_crackdown = draws %>% filter(i == 55) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_emergency_environment_criticized = fin_emergency_criticized - fin_environment_criticized,
  fin_emergency_humanrights_criticized = fin_emergency_criticized - fin_humanrights_criticized,
  fin_emergency_environment_crackdown = fin_emergency_crackdown - fin_environment_crackdown,
  fin_emergency_humanright_crackdown = fin_emergency_crackdown - fin_humanrights_crackdown,
  fin_refugee_environment_criticized = fin_refugee_criticized - fin_environment_criticized,
  fin_refugee_humanright_criticized = fin_refugee_criticized - fin_humanrights_criticized,
  fin_refugee_environment_crackdown = fin_refugee_crackdown - fin_environment_crackdown,
  fin_refugee_humanright_crackdown = fin_refugee_crackdown - fin_humanrights_crackdown
)

@@

```{r practices-contrasts-e}
# Overwrite draws with the appropriate interaction data
draws <- here::here("data", "raw_data", "posterior_draws", "interactions_5e.rds")

@@

contrasts_int <- tibble(
  fin_sd_emergency_criticized = draws %>% filter(i == 56) %>% select(Gamma) %>% pull(),
  fin_sd_emergency_crackdown = draws %>% filter(i == 57) %>% select(Gamma) %>% pull(),
  fin_sd_environment_criticized = draws %>% filter(i == 58) %>% select(Gamma) %>% pull(),
  fin_sd_environment_crackdown = draws %>% filter(i == 59) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_criticized = draws %>% filter(i == 60) %>% select(Gamma) %>% pull(),
  fin_sd_humanrights_crackdown = draws %>% filter(i == 61) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_criticized = draws %>% filter(i == 62) %>% select(Gamma) %>% pull(),
  fin_sd_refugee_crackdown = draws %>% filter(i == 63) %>% select(Gamma) %>% pull()
  ) %>%
  mutate(
  fin_sd_emergency_environment_criticized = fin_sd_emergency_criticized - fin_sd_environment_criticized,
  fin_sd_emergency_humanrights_criticized = fin_sd_emergency_criticized - fin_sd_humanrights_criticized,
  fin_sd_emergency_environment_crackdown = fin_sd_emergency_crackdown - fin_sd_environment_crackdown,
  fin_sd_emergency_humanright_crackdown = fin_sd_emergency_crackdown - fin_sd_humanrights_crackdown,
  fin_sd_refugee_environment_criticized = fin_sd_refugee_criticized - fin_sd_environment_criticized,
  fin_sd_refugee_humanright_criticized = fin_sd_refugee_criticized - fin_sd_humanrights_criticized,
  fin_sd_refugee_environment_crackdown = fin_sd_refugee_crackdown - fin_sd_environment_crackdown,
  fin_sd_refugee_humanright_crackdown = fin_sd_refugee_crackdown - fin_sd_humanrights_crackdown
)
